TODO: A Survey of StarCraft AI Techniques

### 2012-05-04 survey.tex
re-organizing the previous works sections

\subsection{Perception}
XXX Every AI needs to observe the world in order to analyze it and take decisions. In RTS games this task isn't trivial since we have to deal with imperfect information.

@@

\cite{WeberAIIDE11} used a particle model, with a simple linear trajectory update, to track opponent units under fog of war in StarCraft.

@@

\subsection{Strategy}

@@

\subsection{Giving orders}

{\color{ForestGreen}
Explain centralized models (like blackboard) and distributed/hierarchically models.
}

\subsection{Executing orders}

\textbf{Pathfinding}

The most common pathfinding algorithm is A*, but the big problem of this algorithm is the time and  memory consumption, a show-stopper in a real-time environment.

To solve this the search space needs to be reduced as much as possible. One common technique is reducing the tile map search into a navigation graph map. To do this some polygonal triangulations are calculated and abstracted on a grid-based map and this is the TRA* (Triangulation Reduction A*) algorithm\cite{Demyen_2006}.

{\color{ForestGreen}
There are a lot of new pathfinding algorithms. Do we need to review all of them?
}

\textbf{Group behavior}

Craig Reynols introduced algorithmic steering behaviors to simulate the aggregate motion of swarms using procedural animation\cite{Reynolds_1999}. His model describes how a system of multiple agents , each steering according to simple local rules, can produce the collective movement found in flocks of birds. With this behaviours we are able to simulate intelligent squad movements and do tactical moves to flank the opponent in a RTS game\cite{Danielsiek_2008}, improving the survival of our units.

A good alternative to Flocking is using Reciprocal Velocity Obstacles (RVO)\cite{Berg_2008}, since it is easier to control the behavior and they guarantee to prevent collisions. With this algorithm we can move a large squad crossing another squad and avoid all possible collisions between units. This type of techniques are already applied in commercial RTS games like Starcraft 2 or Supreme Commander 2 with great success.

@@

%\subsection{Integration of Domain Knowledge}\label{subsec:domainknowledge}

{\color{blue}
All bots attempt at integrating human domain knowledge in a way or another, be it in the form of build-orders, heuristics, strategies, or by automatically learning from human replays. This has been shown to be key to good performance in bots (for now, as Dave was saying: ``Starcraft AI is like Chess was in the 60s'').

%\subsection{Reasoning with Uncertainty}\label{subsec:uncertainty}

{\color{blue}
I think there are two important aspects of uncertainty in RTS games:
\begin{itemize}
\item First is trying to model uncertainty and try to reduce it (information gathering, and representation of knowledge), this includes scouting, and maintaining good estimates of locations and number of units of the enemy, etc.
\item Second is actually using the uncertain information. Taking decisions like army strength estimation (like to attack or retreat).
\end{itemize}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.9\columnwidth]{figures/levels_abstraction.pdf}
    \caption{RTS AI levels of abstraction and their properties: uncertainty (from intentions and from partial observation) is going higher as the abstraction levels are raising. The timings on the right correspond to an estimate of the duration of a behavior switch in StarCraft.}
    \label{fig:levels-abstraction}
\end{figure*}

%\subsection{Integration of Domain Knowledge}\label{subsec:domainknowledge}
{\color{blue}
All bots attempt at integrating human domain knowledge in a way or another, be it in the form of build-orders, heuristics, strategies, or by automatically learning from human replays. This has been shown to be key to good performance in bots (for now, as Dave was saying: ``Starcraft AI is like Chess was in the 60s'').

%\subsection{Reasoning with Uncertainty}\label{subsec:uncertainty}
{\color{blue}
I think there are two important aspects of uncertainty in RTS games:
\begin{itemize}
\item First is trying to model uncertainty and try to reduce it (information gathering, and representation of knowledge), this includes scouting, and maintaining good estimates of locations and number of units of the enemy, etc.
\item Second is actually using the uncertain information. Taking decisions like army strength estimation (like to attack or retreat).
\end{itemize}

\subsection{Strategy}
XXX Every AI needs to observe the world in order to analyze it and take decisions. In RTS games this task isn't trivial since we have to deal with imperfect information.

@@

\cite{WeberAIIDE11} used a particle model with a simple linear trajectory update to track opponent units under fog of war in StarCraft.

@@

\subsection{Tactics}

@@

\subsection{Units Control}

% {\color{ForestGreen}
% Explain centralized models (like blackboard) and distributed/hierarchically models.
% }
The most common pathfinding algorithm is A*, but the big problem of this algorithm is the time and  memory consumption, a show-stopper in a real-time environment.
To solve this the search space needs to be reduced as much as possible. One common technique is reducing the tile map search into a navigation graph map. To do this some polygonal triangulations are calculated and abstracted on a grid-based map and this is the TRA* (Triangulation Reduction A*) algorithm\cite{Demyen_2006}.

Craig Reynolds introduced algorithmic steering behaviors to simulate the aggregate motion of swarms using procedural animation\cite{Reynolds_1999}. His model describes how a system of multiple agents, each steering according to simple local rules, can produce the collective movement found in flocks of birds. With this behaviors, we are able to simulate intelligent squad movements and do tactical moves to flank the opponent in a RTS game\cite{Danielsiek_2008,SynnaeveMicroCig11}, improving the survival of our units.

A good alternative to Flocking is using Reciprocal Velocity Obstacles (RVO)\cite{Berg_2008}, since it is easier to control the behavior and they guarantee to prevent collisions. With this algorithm, we can move a large squad crossing another squad and avoid all possible collisions between units. This type of techniques are already applied in commercial RTS games like Starcraft 2 or Supreme Commander 2 with great success.

@@
